---
title: "Document Pkg Data"
output: html_notebook
---

# Intro

- This is the recipe I have used to document data for my R packages. The reason I struggled with this is because I failed to clean up my notes on making R packages and so scrambled with this issue till i finally decided to make some template I could follow each time i developed a package.

## Init

- File(s) needs to be copied into extdata before this process can be
accomplished. For R developers this should not be a problem.

## How I add my data
```{r}
fpath <- system.file("extdata", "dat_3.dat", package = "normfluodbf", mustWork = TRUE)
dat_3 <- read.table(fpath) #read data in for use with use_dat
use_data_raw(name=fpath)
usethis::use_data(dat_3)
document()
```

## tidyDenovix
```{r}
#txt
dir = paste0(getwd(),'/data-raw')
fpath = paste0(dir,"/spec.txt")
fpath <- system.file("extdata", "spec.txt", package = "tidyDenovix", mustWork = TRUE)
spec <- utils::read.table(fpath)
use_data_raw(name=fpath)
usethis::use_data(spec)
document()
#rename prep file in data raw

#excel
library(readxl)
dir = paste0(getwd(),'/data-raw')
fpath = paste0(dir,"/rnaspec_1.xlsx")
#fpath <- system.file("extdata", "rnaspec_1.xlsx", package = "tidyDenovix", mustWork = TRUE)
rna1 <- read_excel(fpath)
use_data_raw(name=fpath)
usethis::use_data(rna1)
document()

#csv
dir = paste0(getwd(),'/data-raw')
fpath = paste0(dir,"/rnaspec2018.csv")
#fpath <- system.file("extdata", "rnaspec2018.csv", package = "tidyDenovix", mustWork = TRUE)
rna2 <- read.csv(fpath)
use_data_raw(name=fpath)
usethis::use_data(rna2)
document()

dir = paste0(getwd(),'/data-raw')
fpath = paste0(dir,"/spec.csv")
fpath <- system.file("extdata", "spec.csv", package = "tidyDenovix", mustWork = TRUE)
rna3 <- read.csv(fpath)
use_data_raw(name=fpath)
usethis::use_data(rna3)
document()
```

## Exit

- Rename prep file in data raw
